New_Data_Coherence

### 2019-09-04 Analysis/Category_Tables.Rmd
remove all unneeded packages and clean
Move Figures folder to manuscript
Save tables in capital Tables

```{r}
require(dplyr)
```

@@

write_xlsx(wb, "../manuscript/tables/supplementary_table_S1.xlsx")

@@

write.csv(Cat_Within, "../manuscript/tables/table_1.csv", row.names = FALSE)
```

@@

write_xlsx(msig_sum,"../manuscript/tables/supplementary_table_S2.xlsx")

@@

ggsave("../Figures/Size_Slope_Plot.png", slope_plot, height=5, width=7, units="in", dpi = 600)
```

>>>>

```{r}
library(dplyr) #install.packages("dplyr")
```

@@

write_xlsx(wb, "../manuscript/Tables/supplementary_table_S1.xlsx")

@@

write.csv(Cat_Within, "../manuscript/Tables/table_1.csv", row.names = FALSE)
```

@@

write_xlsx(msig_sum,"../manuscript/Tables/supplementary_table_S2.xlsx")

@@

ggsave("../manuscript/Figures/Size_Slope_Plot.png", slope_plot, height=5, width=7, units="in", dpi = 600)
```

### 2019-09-04 Analysis/Coherence_Calculations_New.Rmd
fix warnings
Save tables in capital Tables

```{r}
library(dplyr)   # install.packages("dplyr")
library(readr)   # install.packages("readr")
```

@@

dir.create("../manuscript/tables")
write.csv(coherence_disease, ".././manuscript/tables/supplementary_table_S3.csv", 
          row.names = FALSE)

>>>>

```{r}
library(dplyr)   # install.packages("dplyr")
library(readr)   # install.packages("readr")
options(stringsAsFactors = FALSE)
```

@@

dir.create("../manuscript/tables")
write.csv(coherence_disease, ".././manuscript/Tables/supplementary_table_S3.csv", 
          row.names = FALSE)
